\textbf{Proposal for bachelor thesis}\\ Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks

### 2025-02-02 paper/chapters/results.tex
Update results.tex to include generalization error data for additional datasets and enhance correlation analysis visuals

\section{Graph Convolutional Networks}
The results of the experiments using Graph Convolutional Networks are shown in Table~\ref{tab:ge_gcn}.

\begin{table}[!ht]
    \centering
    \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
    \hline
    \toprule
        Name & Ave. generalization error & Standard deviation \\ 
    \midrule
        MCF-7 & 0.002249991986900568 & 0.01604018546640873 \\
        MCF-7H & 0.004124999046325684 & 0.02702830731868744 \\
        MOLT-4 & 0.0 & 0.014102176763117313 \\
        MOLT-4H & 0.008624988608062267 & 0.01870434731245041 \\
        Mutagenicity & 0.03765624016523361 & 0.024758048355579376 \\
        MUTAG & 0.13552632927894592 & 0.10957122594118118 \\
        NCI1 & 0.06834375858306885 & 0.0339551605284214 \\
        NCI109 & 0.07212500274181366 & 0.030083369463682175 \\
        NCI-H23 & 0.003218746278434992 & 0.013211547397077084 \\
        NCI-H23H & 0.0006250202422961593 & 0.011396590620279312 \\
        OVCAR-8 & -0.0001249849738087505 & 0.015103230252861977 \\
        OVCAR-8H & 0.0001562476099934429 & 0.013315632939338684 \\
        P388 & 0.008062511682510376 & 0.01043933816254139 \\
        P388H & 0.006343752145767212 & 0.007148966193199158 \\
        PC-3 & 0.0008750140550546348 & 0.012619029730558395 \\
        PC-3H & 0.0001250088243978098 & 0.00780930370092392 \\
        PTC\_FM & 0.12454469501972198 & 0.14246851205825806 \\
        PTC\_FR & 0.08159632235765457 & 0.09593729674816132 \\
        PTC\_MM & 0.12555554509162903 & 0.12687508761882782 \\
        PTC\_MR & 0.058610398322343826 & 0.11794959753751755 \\
        SF-295 & 0.0009687542915344238 & 0.013665653765201569 \\
        SF-295H & 0.004500013776123524 & 0.018203353509306908 \\
        SN12C & 0.0004999935626983643 & 0.017035124823451042 \\
        SN12CH & 0.006718760821968317 & 0.016944456845521927 \\
        SW-620 & 5.9604645663569045e-09 & 0.006674798205494881 \\
        SW-620H & 0.002499997615814209 & 0.008080806583166122 \\
        UACC257 & 0.0022812604438513517 & 0.013034629635512829 \\
        UACC257H & 6.25073880655691e-05 & 0.015311303548514843 \\
        Yeast & 0.0022187530994415283 & 0.01859860308468342 \\
        YeastH & 0.00024999381275847554 & 0.015245940536260605 \\
        PROTEINS\_full & 0.11115662008523941 & 0.5160216689109802 \\
        DD & -0.1750326007604599 & 0.3490835428237915 \\
        ENZYMES & 0.3110416531562805 & 0.06384395807981491 \\
        KKI & 0.04776120185852051 & 0.2546080946922302 \\
        OHSU & 0.39824172854423523 & 0.138640895485878 \\
        Peking\_1 & 0.2980072498321533 & 0.2580110728740692 \\
        COLORS-3 & 0.07568749040365219 & 0.03585537523031235 \\
        SYNTHETIC & -0.41749995946884155 & 0.3929196000099182 \\
        SYNTHETICnew & -0.36250001192092896 & 0.45766785740852356 \\
        Synthie & 0.14562499523162842 & 0.032582689076662064 \\ 
        \bottomrule
    \end{tabular}
    \caption{Generalization error of the GCN model on 57 datasets}
    \label{tab:ge_gcn} % ge -> generalization error
\end{table}

>>>>

\section{Graph Convolutional Networks}
The calculated generalization error of the experiments using Graph Convolutional Networks are shown in Table~\ref{tab:ge_gcn}.

\begin{table}[!ht]
    \centering
    \footnotesize
    \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
    \hline
    \toprule
        Name & Ave. generalization error & Standard deviation \\ 
    \midrule
        AIDS & 0.0081874905154109 & 0.0117165874689817 \\ 
        BZR & 0.0708846226334571 & 0.0609733723104 \\ 
        BZR\_MD & 0.0961788743734359 & 0.1091229766607284 \\ 
        COLORS-3 & 0.06828124076128 & 0.0298492461442947 \\ 
        COX2 & 0.0840000063180923 & 0.1163316890597343 \\ 
        COX2\_MD & 0.0750205665826797 & 0.1105385944247245 \\ 
        DD & 0.0138164404779672 & 0.0569455623626709 \\ 
        DHFR & 0.1413267403841018 & 0.0572429783642292 \\ 
        DHFR\_MD & 0.0547252781689167 & 0.1071747243404388 \\ 
        ENZYMES & 0.1968750059604644 & 0.1035036742687225 \\ 
        ER\_MD & 0.0477907545864582 & 0.0669434815645217 \\ 
        FRANKENSTEIN & 0.0549374930560588 & 0.0326129123568534 \\ 
        KKI & 0.1822761297225952 & 0.3100946843624115 \\ 
        MCF-7 & 0.0019999979995191 & 0.0135001158341765 \\ 
        MCF-7H & 0.003406238509342 & 0.0127300517633557 \\ 
        MOLT-4 & 0.0015624940861016 & 0.0123682264238595 \\ 
        MOLT-4H & 0.0034062266349792 & 0.0167727246880531 \\ 
        MUTAG & 0.1002193242311477 & 0.0946124866604805 \\ 
        Mutagenicity & 0.040156252682209 & 0.0229900479316711 \\ 
        NCI-H23 & 0.0028750181663781 & 0.0120867453515529 \\ 
        NCI-H23H & 0.0005312621360644 & 0.0108473878353834 \\ 
        NCI1 & 0.0832187384366989 & 0.0319501645863056 \\ 
        NCI109 & 0.0711562559008598 & 0.0383276790380477 \\ 
        OHSU & 0.3857143521308899 & 0.2356772273778915 \\ 
        OVCAR-8 & 0.0038125098217278 & 0.0155245345085859 \\ 
        OVCAR-8H & 0.0028437494765967 & 0.0162141937762498 \\ 
        P388 & 0.0043125031515955 & 0.013600654900074 \\ 
        P388H & 0.0070000053383409 & 0.0142645183950662 \\ 
        PC-3 & 0.0024375021457672 & 0.0098565947264432 \\ 
        PC-3H & 0.0060312449932098 & 0.0117860734462738 \\ 
        PROTEINS\_full & 0.0026662945747375 & 0.0525967963039875 \\ 
        PTC\_FM & 0.0923068895936012 & 0.1087017878890037 \\ 
        PTC\_FR & 0.1018810272216796 & 0.1225867569446563 \\ 
        PTC\_MM & 0.088215485215187 & 0.0875236690044403 \\ 
        PTC\_MR & 0.0782608613371849 & 0.0882423818111419 \\ 
        Peking\_1 & 0.2760869860649109 & 0.2045421004295349 \\ 
        SF-295 & 0.0032500028610229 & 0.0157351642847061 \\ 
        SF-295H & 0.0017812550067901 & 0.0091287596151232 \\ 
        SN12C & 0.0003750085888896 & 0.0128499586135149 \\ 
        SN12CH & 0.0031250000465661 & 0.0179813411086797 \\ 
        SW-620 & 0.0014062583213672 & 0.0130064394325017 \\ 
        SW-620H & 0.0014687419170513 & 0.0133227882906794 \\ 
        SYNTHETIC & 0.0120833460241556 & 0.0160114392638206 \\ 
        SYNTHETICnew & 0.1366666555404663 & 0.1849549412727356 \\ 
        Synthie & 0.1234375014901161 & 0.0413857623934745 \\ 
        UACC257 & 0.0011249959934502 & 0.0108615579083561 \\ 
        UACC257H & 0.000843757414259 & 0.0126192783936858 \\ 
        Yeast & 0.0053749978542327 & 0.027795847505331 \\ 
        YeastH & 0.0001875102461781 & 0.0135009009391069 \\ 
    \end{tabular}
    \caption{Generalization error of the GCN model on 49 datasets}
    \label{tab:ge_gcn} % ge -> generalization error
\end{table}

The correlation between the generalization error and the graph parameters are shown in Figure~\ref{fig:correlation_GCN} and Figure~\ref{fig:correlation_ignore_less_than_1000_GCN}.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{images/correlation_GCN.png}
    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Graph Convolutional Network (GCN). Each subplot presents the correlation coefficient between a specific graph property and the generalization error. Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
    \label{fig:correlation_GCN}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{images/correlation_ignore_less_than_1000_GCN.png}
    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Graph Convolutional Network (GCN). Each subplot presents the correlation coefficient between a specific graph property and the generalization error. Only datasets with more than 1000 graphs are considered.}
    \label{fig:correlation_ignore_less_than_1000_GCN}
\end{figure}

\subsection{Discussion}

\section{Simplified Graph Convolution}
The calculated generalization error of the experiments using Simplified Graph Convolution are shown in Table~\ref{tab:ge_sgc}.

\begin{table}[!ht]
    \centering
    \footnotesize
    \begin{tabular}{p{3.5cm}|p{5cm}p{5cm}}
    \hline
    \toprule
        Name & Ave. generalization error & Standard deviation \\ 
    \midrule
        AIDS & 0.0094999792054295 & 0.0067623262293636 \\
        BZR & 0.0398076958954334 & 0.0535244457423687 \\
        BZR\_MD & 0.1050406470894813 & 0.095137633383274 \\
        COLORS-3 & 0.0739687532186508 & 0.0297187566757202 \\
        COX2 & 0.0861333459615707 & 0.0670665428042411 \\
        COX2\_MD & 0.0440740659832954 & 0.1867186874151229 \\
        DD & 0.1082454919815063 & 0.0635362416505813 \\
        DHFR & 0.1035643592476844 & 0.0682980865240097 \\
        DHFR\_MD & 0.0555799715220928 & 0.1178753077983856 \\
        ENZYMES & 0.1837499886751175 & 0.0857001841068267 \\
        ER\_MD & 0.0475622005760669 & 0.0829107165336608 \\
        FRANKENSTEIN & 0.061875008046627 & 0.0329361073672771 \\
        KKI & 0.0291044823825359 & 0.2818436622619629 \\
        MCF-7 & 0.000656247138977 & 0.0137401102110743 \\
        MCF-7H & 0.001156234764494 & 0.0151891019195318 \\
        MOLT-4 & 0.0018124937778338 & 0.0116189513355493 \\
        MOLT-4H & 0.0018437386024743 & 0.0139454510062932 \\
        MUTAG & 0.1163011640310287 & 0.0678915232419967 \\
        Mutagenicity & 0.0481875017285347 & 0.0258940625935792 \\
        NCI-H23 & 0.0031250119209289 & 0.0100476266816258 \\
        NCI-H23H & 5.9604645663569045e-09 & 0.0108693270012736 \\
        NCI1 & 0.0839374884963035 & 0.0166628845036029 \\
        NCI109 & 0.0677187517285347 & 0.0309047140181064 \\
        OHSU & 0.0270329676568508 & 0.2689114809036255 \\
        OVCAR-8 & 0.0021875083912163 & 0.0154096204787492 \\
        OVCAR-8H & 0.0021250010468065 & 0.0172242671251297 \\
        P388 & 0.0042812586762011 & 0.0127577884122729 \\
        P388H & 0.0118749979883432 & 0.0183747168630361 \\
        PC-3 & -0.0001562476099934 & 0.0097229816019535 \\
        PC-3H & 0.000968748354353 & 0.0120369335636496 \\
        PROTEINS\_full & 0.0114296078681945 & 0.0617067217826843 \\
        PTC\_FM & 0.101800300180912 & 0.1584279388189315 \\
        PTC\_FR & 0.102684274315834 & 0.0604767650365829 \\
        PTC\_MM & 0.1027272716164588 & 0.1311521083116531 \\
        PTC\_MR & 0.1173060312867164 & 0.1128198280930519 \\
        Peking\_1 & 0.232065200805664 & 0.290688544511795 \\
        SF-295 & 0.0006874978425912 & 0.0154270688071846 \\
        SF-295H & 0.0021562576293945 & 0.0088528767228126 \\
        SN12C & 0.001562523888424 & 0.0126561466604471 \\
        SN12CH & -6.249547004699707e-05 & 0.0126207722350955 \\
        SW-620 & 0.0008437514188699 & 0.0120212435722351 \\
        SW-620H & 0.0024687468539923 & 0.0140694072470068 \\
        SYNTHETIC & 0.0154166761785745 & 0.0234100967645645 \\
        SYNTHETICnew & 0.1204166635870933 & 0.0984339192509651 \\
        Synthie & 0.1784375011920929 & 0.0635749474167823 \\
        UACC257 & 3.124475551885553e-05 & 0.0105321435257792 \\
        UACC257H & 5.9604645663569045e-09 & 0.0123304584994912 \\
        Yeast & 0.0027187527157366 & 0.0283915027976036 \\
        YeastH & 0.0021875023376196 & 0.0149637833237648 \\
    \end{tabular}
    \caption{Generalization error of the SGC model on 49 datasets}
    \label{tab:ge_sgc} % ge -> generalization error
\end{table}

The correlation between the generalization error and the graph parameters are shown in Figure~\ref{fig:correlation_SGC} and Figure~\ref{fig:correlation_ignore_less_than_1000_SGC}.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{images/correlation_SGC.png}
    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model. Each subplot presents the correlation coefficient between a specific graph property and the generalization error. Colors indicate dataset sizes: blue (<1000 graphs), red (1000-4000 graphs), and green (>4000 graphs).}
    \label{fig:correlation_SGC}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{images/correlation_ignore_less_than_1000_SGC.png}
    \caption{Scatter plots showing the relationship between various graph parameters and the average generalization error of a Simplified Graph Convolution (SGC) model. Each subplot presents the correlation coefficient between a specific graph property and the generalization error. Only datasets with more than 1000 graphs are considered.}
    \label{fig:correlation_ignore_less_than_1000_SGC}
\end{figure}
